### 2020-10-12 ThermalFieldTheory2020/thermal1/thermal1.tex
Add minor tweaks of recent updates

	$\fdv{S}{x(\tau)}$ yields precisely the quantum EOM:
	\begin{equation}
		\fdv{S}{x(\tau)}
		= m\,\pqty{
				-\pdv[2]{}{\tau}
				+ \omega^2
			}\,x(\tau)
	\end{equation}
	After some re-organization, we get the quantum equation for the Green function (which, for such a free theory, is identical to the classical one):
	\begin{equation}
		m\,\pqty{
			-\pdv[2]{}{\tau}
			+ \omega^2
		} \int \DD{x} e^{-S}
			x(\tau)\,x(\tau')
		= \delta(\tau - \tau')
			\int \DD{x} e^{-S},
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		\pqty{
			-\pdv[2]{}{\tau}
			+ \omega^2
		}\, G(\tau,\tau')
		= \frac{1}{m}\, \delta(\tau - \tau'),
	\quad
		G(\tau) = G(\tau,0)
	\end{equation}

>>>>

	$\fdv{S}{x(\tau)}$ yields precisely the quantum EOM:
	\begin{equation}
		\fdv{S}{x(\tau)}
		= m\,\pqty{
				-\pdv[2]{}{\tau}
				+ \omega^2
			}\,x(\tau)
	\end{equation}
	After some re-organization, we get the quantum equation for the Green's function (which, for a free theory, is identical to the classical one):
	\begin{equation}
		m\,\pqty{
			-\pdv[2]{}{\tau}
			+ \omega^2
		} \int \DD{x} e^{-S}
			x(\tau)\,x(\tau')
		= \delta(\tau - \tau')
			\int \DD{x} e^{-S},
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		\pqty{
			-\pdv[2]{}{\tau}
			+ \omega^2
		}\, G(\tau,\tau')
		= \frac{1}{m}\, \delta(\tau - \tau'),
	\quad
		G(\tau) = G(\tau,0)
	\end{equation}
